Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\subsection{Mapping ZLog onto Malacology}
\label{sec:mapping-zlog-onto-malacology}
We evaluate the mapping of ZLog onto Malacology by examining the costs of
utilizing the metadata service as a sequencer, and of propagating interface
changes throughout the cluster using the monitoring service. We have omitted
evaluation of the overhead costs of adding object interfaces themselves due to
lack of space, and the fact that they are heavily tested and used already in
production with acceptable performance, introducing a small constant overhead
per operation without affecting scalability.

@@

\subsection{Load Balancing ZLog Sequencers with Mantle}

>>>>

\subsection{Mapping ZLog onto Malacology}
\label{sec:mapping-zlog-onto-malacology}

We evaluate Malacology by exploring one possible mapping of the ZLog
implementation of CORFU onto Ceph in which we re-use (1) the metadata service
to manage naming and synchronization of the sequencer resource by treating the
resource as an inode, and (2) the monitoring sub-subsystem to distribute and
install application-specific I/O interface required of the CORFU protcool. In
Section~\ref{sec:zlog-balancing} we then demonstrate how the re-use of the inode
abstraction for implementing the sequencer resource enables load balancing policies
to migrate the sequencer resource in heavy-load situation.

@@

\subsection{Load Balancing ZLog Sequencers with Mantle}
\label{sec:zlog-balancing}
